### 2019-05-23 2_metg.tex
Tweak text.

The \emph{minimum effective task granularity}, METG(50\%), for an application $A$ is
the smallest average task granularity (i.e., task duration) such that $A$
achieves overall efficiency of at least 50\%. For example, in
compute-bound applications efficiency can be measured as the
percentage of the available FLOP/s achieved. On Cori with 1.26 TFLOP/s available per Haswell node, METG(50\%) corresponds to
the smallest task granularity achieved while maintaining at least 0.63
TFLOP/s. Absolute (rather than relative) efficiency is preferred
because it better quantifies the performance tradeoff made by
programming systems that reserve processor cores to implement asynchronous operations (such as data movement).

>>>>

The \emph{minimum effective task granularity}, METG(50\%), for an application $A$ is
the smallest average task granularity (i.e., task duration) such that $A$
achieves overall efficiency of at least 50\%. For example, in
compute-bound applications efficiency can be measured as the
percentage of the available FLOP/s achieved. On Cori with 1.26 TFLOP/s available per Haswell node, METG(50\%) corresponds to
the smallest task granularity achieved while maintaining at least 0.63
TFLOP/s. For applications not amenable to being characterized by peak
performance, an application-specific measure of performance can be
used instead (e.g., mesh cells processed per second).
